\hypertarget{biomedical-images-metadatabase}{%
\section{Biomedical Images
MetaDatabase}\label{biomedical-images-metadatabase}}

\hypertarget{about}{%
\subsection{About}\label{about}}

A tool to build an image database with searchable metadata for
biomedical applications.

This project was implemented for the course Programming Lab II, in the
winter semester 2019-2020 as a part of Msc Life Science Informatics
curriculum.

\hypertarget{host-institution}{%
\subsection{Host Institution}\label{host-institution}}

Bonn Aachen International Center for Information Technology, Bonn,
Germany.

\hypertarget{running-the-application}{%
\subsection{Running the Application}\label{running-the-application}}

Run the following directories in a Sequential order: 1.
\textbf{CommandLineInterface} - The application should take several
command line parameters. Example: --import takes an image file name.
--print is an option that prints all meta information on the screen
without doing anything more. 2. \textbf{SQLite} - This application helps
the user to create database objects and interact with them. The user can
provide a directory on which a database object can be based. This
directory should contain image files (.jpg, .jpeg or .png) and
corresponding metadata files (.txt) carrying the same file name. The
images are stored in the database along with the corresponding metadata.
3. \textbf{RestfulAPI} - This application provides a RESTful web service
using Spring. \#\# Note Each directory folder contains a readme that
describes what that part of the application does in more detail.

\hypertarget{built-with}{%
\subsection{Built With}\label{built-with}}

\begin{itemize}
\tightlist
\item
  \href{https://maven.apache.org/}{Maven} - Dependency Management
\end{itemize}

\hypertarget{authors}{%
\subsection{Authors}\label{authors}}

\textbf{Shreya Kapoor} \textbf{Sophia Krix} \textbf{Gemma van der Voort}

\hypertarget{acknowledgments}{%
\subsection{Acknowledgments}\label{acknowledgments}}

\textbf{Dr.~Jens Dorpinghaus} \textbf{Dr.~Sebastian Schaaf}
